\vspace{-1em}
\cvsection{Key Projects}
\begin{cventries}
%\cventry
%	{Founder and Chief Engineer | \textit{Research \& Development}}
%	{Cognitive Interfaces}
%	{Bengaluru, India}
%	{Oct. 2016 - Present}
%	{ \begin{cvitems}
%		\item {3D reconstruction of Indian map using CesiumJS, SketchUp, Digital Globe and OSM.} %\href{https://prakshep.com}{\color{dblue}{\textbf{[\scriptsize POC Website Link]}}}}
%		\item {ASR and NLP with NodeJS backend for interaction in VR mode.}
%		\item {Open data and 3D object visualization using MapServer, Map Tiler, Blender.} %\href{https://maps.prakshep.com}{\color{dblue}{\textbf{[\scriptsize POC Bengaluru City Link]}}}}
%	  \end{cvitems}	
%	}

	\cventry
	{Machine Learning Intern | \textit{Wrappid: Wrappup Inc.'s ASR and Audio Search Platform}}
	{Wrappup Inc.}
	{Dubai, UAE}
	{Jun. 2016 - Sep. 2016}
	{ \begin{cvitems}
		\item {Responsible for end to end development of platform.}
		\item {Designed phoneme recognition and keyword spotting models using SVM and DNN.}
		\item {Developed ASR framework using Python, Bash and C++.}		
	  \end{cvitems}
	}

\cventry
  	{Technical Lead | \textit{Entrepreneurship and Product Development}}
  	{Dice Automations (Early Stage Startup)}
  	{Bengaluru, India}
  	{Dec. 2015 - Feb. 2016}
  	{ \begin{cvitems}
  		\item {Developed product roadmap focusing on Home Automation, Healthcare, Logistics, Retail and Media industry verticals.}
		\item {Principal Engineer for hardware and server backend framework.}
		\item {Deployed a cloud application for IR Voice Remote using Google Voice API and NLP back-end.}
		\end{cvitems}  	
  	}
  	  
\cventry
  	{Researcher | \textit{CTRB Bearing Defect Analyzer - Phase I}}
  	{Jamalpur Locomotive Workshop}
  	{Jamalpur, India}
  	{Jul. 2015 - Sep. 2015}
  	{ \begin{cvitems}
  		\item {Studied different faults and their causes in roller bearings.}
  		\item {Designed a test rig to develop an IoT based sensor module to record vibrational signals for different faults.}
  		\item {Studied BSS to extract vibrational signals of bearing elements in a mixed source problem environment.}
  		\item {Studied the application of ANN, SVM based models to classify signals from good and faulty bearings.}
  	  \end{cvitems}
  	}
\cventry
    {Quarter Finalist | \textit{Development of a stand-alone speech recognition SoC to assist in mail and courier sorting}}
    {Texas Instruments Innovation Challenge India Design Challenge 2015}
    {India}
    {Dec. 2014 - May. 2015}
    {
      \begin{cvitems}
        \item {Designed and fabricated a stand-alone voice recognition system to assist in sorting packages at various hubs.}
        \item {The system was an external attachment with pre-stored address and worked by identifying a spoken word, comparing it with the stored word and releasing an audible beacon upon finding a match. \href{https://www.youtube.com/watch?v=rx7Vyt9G-do}{\color{dblue}{\textbf{[\scriptsize Video Link]}}}}
        \item {Patent filed on its extended application as an external attachment to everyday devices to assist in their location when lost.}
      \end{cvitems} 
    }
\end{cventries}