\vspace{-1em}
\cvsection{Publications}
%\cvsubsection{Conference}
\begin{cventries}
\cventry
{\cvsubsection{Patents}}
{}
{}
{}
{
 \begin{cvlist}
	\item ``Apparatus and method for locating misplaced item,'' \textit{Application number: 3135/DEL/2015}.
 \end{cvlist}
}
\cventry
{\cvsubsection{Journals}}
{}
{}
{}
{\begin{cvlist}
	\item \textbf{Arpit Aggarwal} and Mahesh Chandra, ``Location of Objects using Embedded Speech and Speaker Recognition System,'' \textit{IEEE/ACM Transactions on Audio, Speech, and Language Processing}. \textbf{[\scriptsize Under Review]}
 \end{cvlist}
 }
\cventry
{\cvsubsection{Conferences}}
{}
{}
{}
{\begin{cvlist}
	\item \textbf{Arpit Aggarwal}, Rajeev Kumar, Tanvi Sahay and Mahesh Chandra, ``GuiTones-I: An Audio Visual Database of Monophonic Guitar Tones,'' in \textit{TENCON 2016-2016 IEEE Region 10 Conference}, Nov. 2016. \href{http://ieeexplore.ieee.org/document/7848049}{\color{dblue}{\textbf{[\scriptsize IEEEXplore Link]}}}
	\item \textbf{Arpit Aggarwal}, Tanvi Sahay, Annu Bansal and Mahesh Chandra, ``Grid Search Analysis of nu-SVC for Text-Dependent Speaker-Identiﬁcation,'' in \textit{2015 Annual IEEE India Conference (INDICON)}, Dec. 2015, pp. 1-5. \textbf{[\scriptsize Best Paper Award]} \href{http://ieeexplore.ieee.org/document/7443790}{\color{dblue}{\textbf{[\scriptsize IEEEXplore Link]}}}
	\item Tanvi Sahay, \textbf{Arpit Aggarwal}, Annu Bansal and Mahesh Chandra, ``SVM and ANN: A Comparative Evaluation,'' in \textit{Next Generation Computing Technologies (NGCT), 2015 1st International Conference on}, Sept. 2015, pp. 960-964. \href{http://ieeexplore.ieee.org/document/7375263}{\color{dblue}{\textbf{[\scriptsize IEEEXplore Link]}}}
	\item \textbf{Arpit Aggarwal}, Tanvi Sahay and Mahesh Chandra, ``Performance Evaluation of Artificial Neural Networks for Isolated Hindi Digit Recognition using LPC and MFCC,'' in~\textit{Advanced Computing and Communication Systems, 2015 International Conference on}, Jan. 2015, pp. 1-6. \textbf{[\scriptsize Best Paper Award]} \href{http://ieeexplore.ieee.org/document/7324099}{\color{dblue}{\textbf{[\scriptsize IEEEXplore Link]}}}
\end{cvlist}
}
\end{cventries}




%\begin{cvhonors}
%  \cvhonor
%    {Finalist}
%    {DEFCON 22nd CTF Hacking Competition World Final}
%    {Las Vegas, U.S.A}
%    {2014}
%  \cvhonor
%    {Finalist}
%    {DEFCON 21st CTF Hacking Competition World Final}
%    {Las Vegas, U.S.A}
%    {2013}
%  \cvhonor
%    {Finalist}
%    {DEFCON 19th CTF Hacking Competition World Final}
%    {Las Vegas, U.S.A}
%    {2011}
%  \cvhonor
%    {6th Place}
%    {SECUINSIDE Hacking Competition World Final}
%    {Seoul, S.Korea}
%    {2012}
%\end{cvhonors}
%
%\cvsubsection{Domestic}
%\begin{cvhonors}
%  \cvhonor
%    {3rd Place}
%    {WITHCON Hacking Competition Final}
%    {Seoul, S.Korea}
%    {2015}
%  \cvhonor
%    {Silver Prize}
%    {KISA HDCON Hacking Competition Final}
%    {Seoul, S.Korea}
%    {2013}
%\end{cvhonors}
