\vspace{-1em}
\cvsection{Research Experience}
\begin{cventries}
  \cventry
  {Junior Research Fellow | \textit{Speech Based Access for Agricultural Commodity Price and Weather Information}}
  {MeitY, GoI - BIT Mesra}
  {Ranchi, India}
  {Dec. 2016 - Present}
  { \begin{cvitems}  		
		\item {Setup Asterisk based Voice Server for ASR based IVR.}
  		\item {Collected phonetically rich Hindi (Jharkhandi) audio data of 1500 speakers in real time environment.}
		\item {Extracted real time agricultural commodity prices and weather information through web crawling.}  		
  		\item {Used Kaldi for preparing ASR system and TTS for knowledge delivery.}
  	\end{cvitems}
  }	
    
  \cventry
  {Team Member | \textit{A.T.O.M. - A TOol for Music transcription}}
  {Bachelor's Thesis}
  {Ranchi, India}
  {Aug. 2015 - May 2016} 
  { \begin{cvitems}
     \item {Prepared an audio-visual database of monophonic isolated guitar notes.}
     \item {Performed audio-visual recognition using ASP, CV \& Machine Learning algorithms on MATLAB and Python.}
     \item {Designed a hardware prototype using Raspberry Pi.}
     \item {Developed the back-end architecture using Django, uWSGI, nginx and PostgreSQL on AWS EC2 instance.}
    \end{cvitems}
  } 
    
  \cventry
    {Summer Research Intern | \textit{Study of changes in recognition efficiency of SVM for different free parameters}}
    {Birla Institute of Technology Mesra}
    {Ranchi, India}
    {May. 2015 - Jul. 2015}    
    {
      \begin{cvitems}
        \item {Implemented Support Vector Machines for Spoken Digit Recognition and Text-Dependent Speaker-Identification on MATLAB.}
        \item {Developed a grid search algorithm for mapping changes in accuracy with changing kernels and their respective parameters.}
        \item {Analysed the relation between type of SVM, training:testing ratio and recognition accuracy of the network.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Student | \textit{Feed-forward neural networks for Hindi digit recognition}}
    {Birla Institute of Technology Mesra}
    {Ranchi, India}
    {Oct. 2014 - Nov. 2014}
    {
      \begin{cvitems}
        \item {Studied the basics of Machine Learning \& Artificial Neural Networks.}
        \item {Implemented Feed-forward and Pattern-network on MATLAB for Hindi Digit Recognition.}
      \end{cvitems}
    }
    
\end{cventries}
